Lab2

### 2021-08-05 src/data/DataCleaning.Rmd

```{r clean unemployment data}
d <- d %>%
  select(
    county,
    long_trip,
    cases,
    deaths,
    median_income,
    is_rural,
    unemp_rate,
    density,
    pct_lt17,
    pct_gt65,
    povery_rate
  )
knitr::kable(head(d))
```

>>>>

```{r clean unemployment data}
d <- d %>%
  select(
    county,
    long_trip,
    cases,
    deaths,
    median_income,
    total_pop,
    is_rural,
    unemp_rate,
    density,
    pct_lt17,
    pct_gt65,
    povery_rate
  )
knitr::kable(head(d))
```
